Inspecting {glmnet} performances

### 2020-03-11 analysis/inspect-glmnet-models.Rmd
workflowr::wflow_publish("analysis/inspect-glmnet-models.Rmd")

R.utils::sourceDirectory("R")
library("drake")
library("mlr")
library("glmnet")
library("ggplot2")
library("magrittr")

@@

- {glmnet} does its own internal 10-fold CV optimization when using `cv.glmnet()`.
  It iterates over `lambda` and chooses the most robust values for prediction via parameter `s` in `predict.glmnet()`. Supplying a custom lambda sequence does not make much sense since the internal heuristics are quite good (if one wants to use non-spatial optimization).
- To conduct a spatial optimization, one needs to use `glmnet()` directly. 
  This implementation does not do an internal optimization for `lambda`  and hence `s` can/needs to be tuned directly by the user. Because it is hard to come up with good tuning ranges in this case, one can fit a `cv.glmnet()` on the data and use the borders of the estimated `lambda` as upper and lower borders of the tuning space.

@@

## Train/predict manually for Fold 1 via {glmnet}

@@

@@

>>>>

R.utils::sourceDirectory("R")
library("drake")
library("mlr")
library("glmnet")
library("ggplot2")
library("magrittr")
library("plotmo")

@@

- {glmnet} does its own internal 10-fold CV optimization when using `cv.glmnet()`.
  It iterates over `lambda` and chooses the most robust values for prediction via parameter `s` in `predict.glmnet()`. 
  Supplying a custom lambda sequence does not make much sense since the internal heuristics are quite good (if one wants to use non-spatial optimization).
  See this [stats.stackexchange question](https://stats.stackexchange.com/a/415248/101464) for how lambda defaults are estimated.
- To conduct a spatial optimization, one needs to use `glmnet()` directly. 
  This implementation does not do an internal optimization for `lambda`  and hence `s` can/needs to be tuned directly by the user. 
  Because it is hard to come up with good tuning ranges in this case, one can fit a `cv.glmnet()` on the data and use the borders of the estimated `lambda` as upper and lower borders of the tuning space.

@@

## Train/predict via {glmnet} manually

@@

```{r}
plotres(modf4)
```

```{r}
plot_glmnet(modf4$glmnet.fit)
```

```{r}
plotmo(modf4$glmnet.fit)
```

@@

Let's look at the x values for observation 737:

```{r}
obs_train_f4[737, top_ten_abs]
```

Looks ok.
